The eclipse of ASASSN-21qj

### 2022-12-29 src/tex/ms.tex
[showyourwork] overleaf sync

{\bf Richelle plots}: The photometry shows deeper absorption at bluer wavelengths compared to longer wavelength passbands.
%
This is an indication that the stellar flux is being scattered by particles that are equal to or smaller than the wavelength of light.
%
By plotting the magnitude of the star versus colour (e.g V versus V-I) the particle size and surface density can be determined.
%
Plots of the light curve show reddening consistent with interstellar dust, and this reddening is parameterised with a reddening angle {\bf (Richelle: I'm not sure of the correct name for this!)}

>>>>

{\bf Richelle plots}: The photometry shows deeper absorption at bluer wavelengths compared to longer wavelength passbands.
%
This is an indication that the stellar flux is being scattered by particles that are equal to or smaller than the wavelength of light.
%
By plotting the magnitude of the star versus colour (e.g V versus V-I) the particle size and surface density can be determined.
%
Plots of the light curve show reddening consistent with interstellar dust, and this reddening is parameterised with a reddening angle {\bf (Richelle: I'm not sure of the correct name for this!)}.
%
The reddening angle for photometry during the eclipse is shown in Figure~\ref{fig:reddenangle}.
%
The measured angle of 59 degrees is consistent with sub-micron sized dust similar in composition to interstellar medium material REF REF RICHELLE.

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/v_vi_fit_eclipse_aavso.pdf}
\caption{Plot of V versus V-I colour as measured from AAVSO data. The reddening angle is determined with a straight line fit to the data.}
        \label{fig:reddenangle}
    \end{centering}
\end{figure}
